|

### 2023-04-08 paper.Rmd

Data collection resulted in a total of `r nrow(filter(vi_survey, !attention_check))` lineup evaluations, `r nrow(filter(vi_survey, type == "polynomial", !attention_check))` for the non-linearity model, and `r nrow(filter(vi_survey, type == "heteroskedasticity", !attention_check))` for the heteroskedasticity model. This was done in three collection periods, called I, II, III, with `r 160 * 18`, `r 150 * 18` and `r 133 * 18 - nrow(filter(vi_survey, null_lineup, !attention_check))` lineups evaluated by 160, 150 and 133 participants, respectively. There were `r nrow(filter(vi_survey, attention_check))` attention check lineups used to filter false participant attempts. To estimate $\alpha$ for calculating statistical significance there were `r nrow(filter(vi_survey, null_lineup, !attention_check))` evaluations of null lineups. Neither the attention checks nor null lineups were used for the subsequent analysis. The de-identified data, `vi_survey`,  is made available in the R package, `visage`.

For clarity and consistency, the analysis in Sections \ref{power-analysis}-\ref{hetero-analysis}, uses only on results from lineups generated with uniform fitted values, a total of `r length(unique(pull(filter(vi_survey, !attention_check, !null_lineup, x_dist == "uniform"), unique_lineup_id)))` lineups and `nrow(filter(vi_survey, !attention_check, !null_lineup))` evaluations. More evaluations were made using the uniform fitted value distribution, and it avoids potentially confounding results of the analysis by combining values from different power curves. We also expect that visual patterns are more clearly visible when the fitted value distribution is uniform. The results in Section \ref{effect-of-fitted-value-distributions} examine the effect of fitted value distribution on power.

>>>>

Data collection used a total of `r vi_survey %>% count(unique_lineup_id) %>% nrow()` lineups, and resulted in a total of `r nrow(filter(vi_survey, !attention_check))` evaluations from `r vi_survey %>% count(set, exp) %>% nrow()` participants. Roughly half corresponded to the two models, non-linearity and heteroskedasticiy, and the three collection periods had similar numbers in each. <!-- `r nrow(filter(vi_survey, type == "polynomial", !attention_check))` for the non-linearity model, and `r nrow(filter(vi_survey, type == "heteroskedasticity", !attention_check))` for the heteroskedasticity model. This was done in three collection periods (I, II, III), with `r 160 * 18`, `r 150 * 18` and `r 133 * 18 - nrow(filter(vi_survey, null_lineup, !attention_check))` lineups evaluated by 160, 150 and 133 participants, respectively.--> Each participant received two of the `r vi_survey %>% filter(attention_check) %>% count(unique_lineup_id) %>% nrow()` attention check lineups which were used to filter results of participants who were clearly not making an honest effort (only `r vi_survey %>% filter(attention_check, !detect) %>% count(exp, set) %>% nrow()` of `r vi_survey %>% count(set, exp) %>% nrow()`). To estimate $\alpha$ for calculating statistical significance (see Section \ref{sig}) there were `r nrow(filter(vi_survey, null_lineup, !attention_check))` evaluations of `r vi_survey %>% filter(null_lineup, !attention_check) %>% count(unique_lineup_id) %>% nrow()` null lineups. Neither the attention checks nor null lineups were used for the subsequent analysis. The de-identified data, `vi_survey`,  is made available in the R package, `visage`.

The data was collected on lineups constructed from four different fitted value distributions: uniform, normal, skewed and discrete. More data was collected on the uniform (each evaluated by 11 participants) than the others (each evaluated by 5 participants). The analysis in Sections \ref{power-analysis}-\ref{hetero-analysis}, uses only results from lineups generated with uniform fitted values, a total <!--of `r length(unique(pull(filter(vi_survey, !attention_check, !null_lineup, x_dist == "uniform"), unique_lineup_id)))` lineups and--> `r nrow(filter(vi_survey, !attention_check, !null_lineup, x_dist == "uniform"))` lineup evaluations. This was decided in order to compare the conventional and visual test performance for an optimal scenario. Section \ref{effect-of-fitted-value-distributions} examines how the results may be affected if the fitted value distribution was different.
